### 2016-03-31 chapters/abstract.tex
todos are now in the pdf
rewrote the abstract

Variability management is an essential part of working on product lines.
This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
To further simplify the process of product configuration out of software product-lines, feature models are used to describe the set of features and constraints contained in a given software product-line. This paper proposes a method for automatically generating feature models out of descriptive files and naming conventions.

>>>>

Variability management is an essential part of working on product lines. Feature models are an established tool to describe the set of features and constraints contained in a given software product-line, thus showing the variability. Feature models also facilitate configuration of product lines. However, for most software product lines there exists no feature model. This paper proposes a method for automatically generating feature models out of the structure of given source code and naming conventions.

Furthermore, an alternative method of configuration based on questionnaires is developed in this work. It enables users or customers to configure a product on their own. Also, it allows experts to design the questionnaires according to their domain knowledge during implementation of the product line.
